---
title: "R_Proficiency_HW"
author: "Yiran Zhang"
date: "2025-02-06"
output: html_document
---

```{r}
library(tidyverse)
```

-   Load the mob analysis data

```{r}
mob <- read.csv("https://raw.githubusercontent.com/wellsdata/CompText_Jour/main/data/mob_analysis_data.csv")
```

-   Describe the number of rows and columns in the dataset

```{r}
nrow(mob)
ncol(mob)
```

-Create a table that displays a count of the top 15 newspaper entries

```{r}

Newspaper <- mob %>%
  filter(!is.na(Newspaper)) |>
  group_by(Newspaper) |>
  count(Newspaper) |>
  arrange(desc(n)) |>
  head(n = 15)

Newspaper

```

-Create a table that counts the different entries in the "keyword" column

```{r}
keyword <- mob %>%
  count(keyword) %>%
  group_by(keyword) %>%
  arrange(desc(n))

keyword

```

-Create a table that counts all entries by year

```{r}
years <- mob %>%
  count(Year) %>%
  group_by(Year) %>%
  arrange(desc(n))

years
```

-Create a simple column ggplot chart that shows the total entries by year

```{r}
 mob %>%
    count(Year) %>%
    group_by(Year) %>%
 ggplot(aes(x = Year, y = n, fill = n)) +
  geom_col(position = "dodge") +
  theme(legend.position = "none") +
  labs(title = "Total Entries by Year",
       y="Numbers",
       x="Count")
```

Summary: I found that this dataset consists of 3,836 reports. The top entries come from The Birmingham Age-Herald Magazine, with 118 reports. The key terms in these reports include "mob", "masked", "mobs", and "masked men". The trend figure shows a bimodal pattern, with two peaks around the 1860s and 1900s. And the highest number of crime reports is in 1903, with a total of 246 reports. The main flaw I found about the datasest is the redundancy of key words. For example, mob and mobs represent the same concept, but are coded as two different and separate topics.
