---
title: "Metadata"
author: "Yiran Zhang"
date: "2025-02-12"
output: html_document
---

Class exercise to import your project data into R --Create a folder called "project" in your code folder --Save this file to the "project" folder --Move your Nexis spreadsheet to the folder --Create a project file: File \| New Project \| \*\*\* select Existing folder \| "project" --After project.Rproj launches, then launch this file, metadata.Rmd, and complete the tutorial

**By doing this, you avoid the ring of hell where R can't find your data**

#load tidyverse, janitor, rio

```{r}

library(tidyverse)
library(janitor)
library(rio)
```

#Import your data

```{r}

project <- rio::import("Results list for__4B movement_.XLSX")

# bmore_final  <-  rbind (bmore1,bmore2) 合并两个数据表格
```

# Clean names

```{r}
project <- project |> 
  clean_names()

```

# fix date

```{r}
project <- project |> 
  mutate(date = as.Date(strptime(published_date, format = "%B %d, %Y %A")))

project$year <- year(project$date)

```

# My claude.ai query and reply:

Q: In r, i need to create a new properly formatted date column from a "published_date" column with character data that looks like this: "January 14, 2025 Tuesday", - how do I transform it into a date format?

A: You can use the as.Date() function along with strptime() to convert that date format. Here's how:

df \<- df \|\> mutate(new_date = as.Date(strptime(published_date, format = "%B %d, %Y %A")))

The format string specifies:

%B - full month name (January) %d - day of the month (14) %Y - 4-digit year (2025) %A - full weekday name (Tuesday)

This will create a proper Date column that you can use for analysis and plotting. The resulting date will be in the standard format "2025-01-14".

#   Describe the number of rows and columns in the dataset

```{r}
print(paste0("This dataset has", nrow(project), " rows and ", ncol(project), " columns."))
```

#   Create a table that displays a count of the top 20 newspaper_city entries. Filter out the NA values

```{r}
News_city <- project %>%
  filter(!is.na(publication_location)) |>
  group_by(publication_location) |>
  count(publication_location) |>
  arrange(desc(n)) |>
  head(n = 15)

News_city

countries <- project %>%
  filter(!is.na(countries)) |>
  group_by(countries) |>
  count(countries) |>
  arrange(desc(n)) |>
  head(n = 15)

countries

## Hi professor, I did not find newspaper_city column in my dataset. So I used publication_location and countries to answer this question.


```

#   Create a table that counts all entries by year. 
```{r}

Years <- project %>% 
  filter(!is.na(year)) |>
  count(year) %>% 
  group_by(year) %>% 
  arrange(desc(year))
head(Years)

```

#   Create a simple column ggplot chart that shows the total entries by year

```{r}
ggplot(Years,aes(x = year, y = n,
             fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
#This is your title sequence
  labs(title = "4B Movement Reports in the North America by Year",
       subtitle = "Source: NexisUni",
       caption = "Graphic by Yiran Zhang, 2-16-2025",
       y="Number of Reports",
       x="Year")
```

# Table and charts by dates, not years
```{r}

Dates <- project %>% 
  filter(!is.na(date)) |>
  count(date) %>% 
  group_by(date) %>% 
  arrange(desc(date))
head(Dates)

```

```{r}
ggplot(Dates,aes(x = date, y = n,
             fill = n)) +
  geom_col(position = "dodge") + 
  theme(legend.position = "none") +
  scale_x_date(limits = as.Date(c("2023-01-01", "2025-02-15"))) +
  labs(title = "4B Movement Reports in the North America by Dates",
       subtitle = "Reports during 2023-2025: Source: NexisUni",
       caption = "Graphic by Yiran Zhang, 2-16-2025",
       y="Number of Reports",
       x="dates")
```


#   Memo
I found that the 4B movement is a pretty new topic in North America and only received attention since 2024, during the presidential election. Speaking of location, more than half of the reports come from America, while others are from Canada and Mexico.

I found quite a few flaws in this dataset. First, there are several duplicate reports. That is, some of the news are recorded more than once in the dataset. Second, there are a lot of missing values in key variables, such as countries and publication_location. Third, the coding for these reports is inconsistent. For example, some locations are coded as cities, such as NY or LA, while most are coded as countries, such as the US or international.

My question is: I wonder how to deal with the missing values warning when making charts.
